
---
title: "Group_06"
output:
  html_document: default
  pdf_document: default
date: '2022-03-11'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,comment = NA, message = FALSE, warning = FALSE)
```

```{r libraries}
library(ggplot2)
library(utils)
library(tidyverse)
library(skimr)
library(GGally)
library(janitor)
library(sjPlot)
library(jtools)
library(knitr)
```

# Question {#sec:que}

question of interest:

Which properties of films influence whether they are rated by IMDB as greater than 7 or 
not?

# Tidy data {#sec:tidy}

According to the dataset6 with 2847 films, we choose the variables of year, length, budget, votes and genre as explanatory variables to analyse how these variables affect ratings of films.

Create column with "good" for ratings > 7 and "bad" for ratings <= 7 

```{r import and wrangle data}
# import data
films <- read.csv("C:/Users/danci/Desktop/Uni stuff/Term 2/5085 Data Analysis Skills/Group presentation project/Datasets-20220307/dataset6.csv")
# create column with "good" for ratings > 7 and "bad" for ratings <= 7 
films <- films %>% 
  mutate(rank = cut(rating,breaks=c(0,7,10),labels=c("bad","good")))

```

# Summary statistics of each variable {#sec:summary}

summary , pairwise covariance and boxplots

```{r}
# view data
glimpse(films)
# numerical summaries
films %>% 
  skim()
# turn genre into a categorical variable
films <- films %>% 
  mutate(genre = as.factor(genre))
# There's some missing data for length. Remove those points? Replace them with median length? Replace with median length for that genre?
# check baseline categories for each categorical variable
levels(films$genre)  # baseline = action
levels(films$rank)   # baseline = bad
```


```{r explore data}
# check for collinearity (nothing obvious)
films %>% 
  select(year,length,budget,votes) %>% 
  ggpairs(films)

# look at rank with year (nothing super obvious)
ggplot(films,aes(y=year,fill=rank))+
  geom_boxplot()+
  labs(title="Year")
# look at rank with length (lots of outliers for bad and some overlap of IQR, but looks like shorter may be better)
ggplot(films,aes(y=length,fill=rank))+
  geom_boxplot()+
  labs(title="Film length")
# look at rank with budget (overlap of IQR, but bigger budget seems to be good)
ggplot(films,aes(y=budget,fill=rank))+
  geom_boxplot()+
  labs(title="Budget")
# look at rank with votes (lots of outliers- would need to remove to see how this affects the response)
ggplot(films,aes(y=votes,fill=rank))+
  geom_boxplot()+
  labs(title="Number of votes")
# look at rank with genre (seems like animation, comedy, documentary and short films are more likely to be good, whereas action, drama and romance more likely to be bad)
films  %>% 
  tabyl(genre, rank) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns() %>%  # To show original counts
  knitr::kable()
ggplot(films, aes(x= rank,  y = ..prop.., group=genre, fill=genre)) + 
    geom_bar(position="dodge", stat="count") +
    labs(y = "Proportion",title="Proportions of good and bad films by genre")
# not a usual plot but interesting to see the categories against each other a little easier
ggplot(films,aes(x=genre,y=rank,col=rank))+
  geom_jitter()+
  labs(title="Number of good and bad films by genre")
```


# Modle fitting {#sec:est1}

fit model with all variables

```{r}
head(films)
##fit model with all variables
mod.films<-glm(rank~year+length+budget+votes+genre,data=films, family = binomial(link = "logit"))

summary <- mod.films %>%
  summ() 

summary$coeftable %>% 
  kable(digits = 2,format = "html", table.attr = "style='width:60%;'")

```

stepwise select model

```{r}
##stepwise select model
mod.films %>%
  step() 


```

remove variable "votes" and fit the model again

```{r}
##because the p-value of votes is not significant, so remove votes
mod.films2 <-glm(rank~year+length+budget+genre,data=films, family = binomial(link = "logit"))

summary <-mod.films2 %>%
  summ() 
  
summary$coeftable %>% 
  kable(digits = 2,format = "html", table.attr = "style='width:60%;'")
```

calculate the odds scale the regression coefficients

```{r}
## calculate the odds scale the regression coefficients
plot_model(mod.films2, show.values = TRUE,
title = "", show.p = TRUE,value.offset = 0.25)
```

calculate the estimated probabilities

```{r}
## calculate the estimated probabilities
plot_model(mod.films2, type = "pred", title = "",
axis.title = c("", "Probability of good film"))
```

add the estimates of the log-odds,odds,probability to our data set

```{r}
## add the estimates of the log-odds,odds,probability to our data set
films2 <- films[,-c(5)]
films3 <- na.omit(films2)
films3 <- films3 %>%
                  mutate(logodds.rank = predict(mod.films2))
films3 <- films3 %>%
                  mutate(odds.rank = exp(logodds.rank))
films3 <- films3 %>%
                  mutate(probs.rank = fitted(mod.films2))
glimpse(films3)
```

calculate the confidence interval of log-odds and odds 

```{r}
##calculate the confidence interval 
logodds <- mod.films2 %>%
           summary() %>%
           coef()

## the CI for year
# for logodds
year.logodds.lower <- logodds["year",  "Estimate"] - 
                      1.96 * logodds["year", "Std. Error"]

year.logodds.upper <- logodds["year", "Estimate"] + 
                      1.96 * logodds["year", "Std. Error"]
year.CI<-c(year.logodds.lower,year.logodds.upper)
# for odds
year.odds.lower <- exp(year.logodds.lower)
year.odds.upper <- exp(year.logodds.upper)
year.odd.CI<-c(year.odds.lower,year.odds.upper)



## the CI for length
# for logodds
length.logodds.lower <- logodds["length",  "Estimate"] - 
                      1.96 * logodds["length", "Std. Error"]

length.logodds.upper <- logodds["length", "Estimate"] + 
                      1.96 * logodds["length", "Std. Error"]
length.CI<-c(length.logodds.lower,length.logodds.upper)
# for odds
length.odds.lower <- exp(length.logodds.lower)
length.odds.upper <- exp(length.logodds.upper)
length.odd.CI<-c(length.odds.lower,length.odds.upper)



## the CI for budget
# for logodds
budget.logodds.lower <- logodds["budget",  "Estimate"] - 
                      1.96 * logodds["budget", "Std. Error"]

budget.logodds.upper <- logodds["budget", "Estimate"] + 
                      1.96 * logodds["budget", "Std. Error"]
budget.CI<-c(budget.logodds.lower,budget.logodds.upper)
# for odds
budget.odds.lower <- exp(budget.logodds.lower)
budget.odds.upper <- exp(budget.logodds.upper)
budget.odd.CI<-c(budget.odds.lower,budget.odds.upper)



## the CI for genreAnimation 
# for logodds
genreAnimation.logodds.lower <- logodds["genreAnimation",  "Estimate"] - 
                      1.96 * logodds["genreAnimation", "Std. Error"]

genreAnimation.logodds.upper <- logodds["genreAnimation", "Estimate"] + 
                      1.96 * logodds["genreAnimation", "Std. Error"]
genreAnimation.CI<-c(genreAnimation.logodds.lower,genreAnimation.logodds.upper)
# for odds
genreAnimation.odds.lower <- exp(genreAnimation.logodds.lower)
genreAnimation.odds.upper <- exp(genreAnimation.logodds.upper)
genreAnimation.odd.CI<-c(genreAnimation.odds.lower,genreAnimation.odds.upper)



## the CI for genreComedy 
# for logodds
genreComedy.logodds.lower <- logodds["genreComedy",  "Estimate"] - 
                      1.96 * logodds["genreComedy", "Std. Error"]

genreComedy.logodds.upper <- logodds["genreComedy", "Estimate"] + 
                      1.96 * logodds["genreComedy", "Std. Error"]
genreComedy.CI<-c(genreComedy.logodds.lower,genreComedy.logodds.upper)
# for odds
genreComedy.odds.lower <- exp(genreComedy.logodds.lower)
genreComedy.odds.upper <- exp(genreComedy.logodds.upper)
genreComedy.odd.CI<-c(genreComedy.odds.lower,genreComedy.odds.upper)



## the CI for genreDocumentary 
# for logodds
genreDocumentary.logodds.lower <- logodds["genreDocumentary",  "Estimate"] - 
                      1.96 * logodds["genreDocumentary", "Std. Error"]

genreDocumentary.logodds.upper <- logodds["genreDocumentary", "Estimate"] + 
                      1.96 * logodds["genreDocumentary", "Std. Error"]
genreDocumentary.CI<-c(genreDocumentary.logodds.lower,genreDocumentary.logodds.upper)
# for odds
genreDocumentary.odds.lower <- exp(genreDocumentary.logodds.lower)
genreDocumentary.odds.upper <- exp(genreDocumentary.logodds.upper)
genreDocumentary.odd.CI<-c(genreDocumentary.odds.lower,genreDocumentary.odds.upper)



## the CI for genreDrama 
# for logodds
genreDrama.logodds.lower <- logodds["genreDrama",  "Estimate"] - 
                      1.96 * logodds["genreDrama", "Std. Error"]

genreDrama.logodds.upper <- logodds["genreDrama", "Estimate"] + 
                      1.96 * logodds["genreDrama", "Std. Error"]
genreDrama.CI<-c(genreDrama.logodds.lower,genreDrama.logodds.upper)
# for odds
genreDrama.odds.lower <- exp(genreDrama.logodds.lower)
genreDrama.odds.upper <- exp(genreDrama.logodds.upper)
genreDrama.odd.CI<-c(genreDrama.odds.lower,genreDrama.odds.upper)




## the CI for genreRomance 
# for logodds
genreRomance.logodds.lower <- logodds["genreRomance",  "Estimate"] - 
                      1.96 * logodds["genreRomance", "Std. Error"]

genreRomance.logodds.upper <- logodds["genreRomance", "Estimate"] + 
                      1.96 * logodds["genreRomance", "Std. Error"]
genreRomance.CI<-c(genreRomance.logodds.lower,genreRomance.logodds.upper)
# for odds
genreRomance.odds.lower <- exp(genreRomance.logodds.lower)
genreRomance.odds.upper <- exp(genreRomance.logodds.upper)
genreRomance.odd.CI<-c(genreRomance.odds.lower,genreRomance.odds.upper)



## the CI for genreShort 
# for logodds
genreShort.logodds.lower <- logodds["genreShort",  "Estimate"] - 
                      1.96 * logodds["genreShort", "Std. Error"]

genreShort.logodds.upper <- logodds["genreShort", "Estimate"] + 
                      1.96 * logodds["genreShort", "Std. Error"]
genreShort.CI<-c(genreShort.logodds.lower,genreShort.logodds.upper)
# for odds
genreShort.odds.lower <- exp(genreShort.logodds.lower)
genreShort.odds.upper <- exp(genreShort.logodds.upper)
genreShort.odd.CI<-c(genreShort.odds.lower,genreShort.odds.upper)



## CI for logodds of variables:
CI.logodds<-rbind(year.CI,length.CI,budget.CI,genreAnimation.CI,genreComedy.CI,genreDocumentary.CI,genreDrama.CI,genreRomance.CI,genreShort.CI)
colnames(CI.logodds)<-c("2.5%","97.5%")
CI.logodds


## CI for odds of variables:
CI.odds<-rbind(year.odd.CI,length.odd.CI,budget.odd.CI,genreAnimation.odd.CI,genreComedy.odd.CI,genreDocumentary.odd.CI, genreDrama.odd.CI, genreRomance.odd.CI ,genreShort.odd.CI)
colnames(CI.odds)<-c("2.5%","97.5%")
CI.odds






















